Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-03-26 ident_manu.Rnw
table 5 added

latex( 
  totab[, -c(1, 2)],
  file = '',
  rowlabel = 'Selections by state variable',
  caption = cap_val,
  caption.loc = 'top',
  size = 'scriptsize',
  label = 'tab:heurist3',
  rowname = sels,
  rgroup = unique(stts),
  n.rgroup = as.numeric(table(stts)),
  colheads = colnms
  )
@

>>>>

latex( 
  totab[, -c(1, 2)],
  file = '',
  rowlabel = 'Selections by state variable',
  caption = cap_val,
  caption.loc = 'top',
  size = 'scriptsize',
  label = 'tab:heurist3',
  rowname = sels,
  rgroup = unique(stts),
  n.rgroup = as.numeric(table(stts)),
  colheads = colnms
  )

% calibration table, do
<<calib, eval = T, cache = F>>=

library(tidyverse)
library(lubridate)
source("R/funcs.R")

load(file = 'data/tocal_all.RData')
load(file = 'data/cals.RData')

# starting rmse
strt <- cals[[1]]$mat[1,] %>% 
  .[length(.)]
# 72.13955

idpars <- get_cmbs(tocal_all, 'O2', coll = T, errs = T, pert = 0.5)

colerr <- get_cmbs(tocal_all, 'O2') %>% 
  lapply(function(x) c(x$coll, mean(x$errs), length(x$errs))) %>% 
  do.call('rbind', .) %>% 
  data.frame %>% 
  rownames_to_column %>% 
  rename(
    heurist = rowname, 
    coll = X1,
    avee = X2,
    nprm = X3
  )

levs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'top', 'cattop')
labs <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton', 'Independent of category', 'Equally within category')
caldat <- lapply(cals, function(x) c(x$value, nrow(x$mat))) %>% 
  do.call('rbind', .) %>% 
  data.frame %>% 
  rownames_to_column %>% 
  rename(
    heurist = rowname, 
    rmse = X1, 
    its = X2
  ) %>% 
  left_join(colerr, by = 'heurist') %>% 
  select(heurist, coll, nprm, avee, its, rmse) %>% 
  mutate(
    heurist = factor(heurist, levels = levs, labels = labs),
    coll = ifelse(is.na(coll), 1, coll),
    coll = sapply(coll, scinot),
    nprm = sapply(nprm, scinot),
    its = sapply(its, scinot),
    rmse = sapply(rmse, scinot), 
    avee = sapply(avee, scinot)
    ) %>% 
  arrange(heurist)

# pairs(caldat[, -1])
totab <- caldat
cap_val <- 'Results of model calibration to observed \\ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third). The collinearity values ($\\gamma$) and parameters of each subset are from \\cref{tab:heurist1,tab:heurist2,tab:heurist3}.  Mean L1 is the average of sensitivity values (\\cref{l1}) for the subset.  $RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.'
colnms <- c('$\\gamma$', '$n$ parameters', 'mean L1', 'Iterations', '$RMSE$')

latex( 
  totab[, -1],
  file = '',
  rowlabel = 'Selection heuristic',
  caption = cap_val,
  caption.loc = 'top',
  size = 'scriptsize',
  label = 'tab:calib',
  rowname = totab$heurist,
  rgroup = c('1', '2', '3'),
  n.rgroup = c(5, 1, 1),
  colheads = colnms
  )

### 2017-03-26 ident_manu.tex
table 5 added

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Fri Mar 17 14:00:58 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4e88d0837d798238902ff4eb6348b72e9143c557}{4e88d0837d798238902ff4eb6348b72e9143c557}}

@@

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Sun Mar 26 14:18:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}{4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}}

@@

% calibration table, do
%latex.default(totab[, -1], file = "", rowlabel = "Selection heuristic",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:calib", rowname = totab$heurist, rgroup = c("1",         "2", "3"), n.rgroup = c(5, 1, 1), colheads = colnms)%
\begin{table}[!tbp]
{\scriptsize
\caption{Results of model calibration to observed \ac{do} for each of seven parameter subsets selected by sensitivity within each parameter category (first), independent of category (second), and equally within each category (third). The collinearity values ($\gamma$) and parameters of each subset are from \cref{tab:heurist1,tab:heurist2,tab:heurist3}.  Mean L1 is the average of sensitivity values (\cref{l1}) for the subset.  $RMSE$ shows the final error comparing observed and model output after the specified number of iterations for optimization.\label{tab:calib}} 
\begin{center}
\begin{tabular}{llllll}
\hline\hline
\multicolumn{1}{l}{Selection heuristic}&\multicolumn{1}{c}{$\gamma$}&\multicolumn{1}{c}{$n$ parameters}&\multicolumn{1}{c}{mean L1}&\multicolumn{1}{c}{Iterations}&\multicolumn{1}{c}{$RMSE$}\tabularnewline
\hline
{\bfseries 1}&&&&&\tabularnewline
~~Optics&$3.87$&$3$&$2.81\times 10^{-4}$&$14$&$72.14$\tabularnewline
~~Organic Matter&$8.61$&$5$&$3.18\times 10^{-3}$&$154$&$68.7$\tabularnewline
~~Phytoplankton&$3.97$&$7$&$0.02$&$270$&$68.72$\tabularnewline
~~Temperature&$1$&$1$&$0.02$&$6$&$71.76$\tabularnewline
~~Zooplankton&$5.2$&$4$&$0.03$&$99$&$71.22$\tabularnewline
\hline
{\bfseries 2}&&&&&\tabularnewline
~~Independent of category&$6.81$&$8$&$0.03$&$850$&$67.05$\tabularnewline
\hline
{\bfseries 3}&&&&&\tabularnewline
~~Equally within category&$5.22$&$7$&$0.03$&$690$&$67.67$\tabularnewline
\hline
\end{tabular}\end{center}}
\end{table}
